\documentclass{article}

\usepackage{titling}
\usepackage{titlesec}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}

\titleformat{\section}
{\bfseries\huge}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\bfseries\large}
{$\bullet$}
{1em}
{}
 
\renewcommand{\maketitle}{
    \begin{center}
    {\huge\bfseries\theauthor}
    \vspace{.25em}


    104 Catherine Dr, Luling, LA 70070 --- cwiggins0217@protonmail.com --- (985) 224-9012 --- https://github.com/cwiggins123
    \end{center}
}

\begin{document}

\title{Resume}
\author{Christopher Wiggins}
\maketitle

\section{Education}
\subsection{University of Louisiana at Lafayette}

\begin{itemize}
    \item B.S. Informatics/Systems Administration
    \item Graduated: May 2021
\end{itemize}

\section{Experience}
\subsection{Professional Experience}
\begin{enumerate}
  \item IT Technician --- T. Baker Smith, LLC. May 26, 2022 - November 17, 2022
    \begin{itemize}
	    \item General help desk/desktop support for the firm. First-tier help with all tickets, office 365, hardware and networking troubleshooting, including Autocad. Active directory administration.
    \end{itemize}
\item Desktop Support Technician --- TEKSystems July 2021 - February 2022
    \begin{itemize}
        \item Desktop Support for LCMC Health. Supported users with on-field device and networking troubleshooting, constructed medical carts for UMC Hospital New Orleans, moved executives into new offices downtown.
		\item IS Analyst for Ochsner Health. Responsible for on-field end-user ipad troubleshooting for language translation. Assisted with Learnsoft and Microsoft Active Directory tech support tickets.
    \end{itemize}
\end{enumerate}
\subsection{Personal Projects}
\begin{enumerate}
    \item Home Server --- TrueNAS
        \begin{itemize}
            \item TrueNAS scale running on an HP z820 workstation, hardware customized by myself,
                running services like nextcloud, etc. in docker containers, and virtualized debian
                server for minecraft.
        \end{itemize}
    \item Workstation --- Linux and BSD
        \begin{itemize}
            \item Fedora linux workstation with custom linux kernel for microsoft surface pro 4
            \item customized Slackware linux on thinkpad t430
            \item customized Fedora server on thinkpad w520
        \end{itemize}
\end{enumerate}

\section{Skills}

\subsection{Programming}

Java, Python, SQL, BASH, Powershell
\subsection{Networking and Systems Administration}

TCP/IP, Debian/Ubuntu, Red Hat, Windows 10, Ansible, Microsoft Office 365, Active Directory


CCNA certification in progress
%compTIA: A+, Networking+, Security+, CCNA


\section{Misc. experience}
  \subsection{Boy Scouts of America: Leadership experience and training}
    \begin{itemize}
      \item Served terms as Senior Patrol Leader and Patrol Leader
      \item Eagle Scout, January 2017
      \item National Youth Leadership Training, Summer 2016
      \item Order of the Arrow (BSA Honor Society)
    \end{itemize}
  \subsection{Chi Alpha Christian Ministries}
    \begin{itemize}
      \item Served as a small group leader in the ministry
    \end{itemize}

\end{document}
